When does vapor pressure deficit drive or reduce evapotranspiration?

### 2017-10-03 doc/paper/vpd_et_paper.tex
added table to latex document and formatted, now just need to get back to writing, shoudl really try to get this done tomorrow

\begin{table}
\caption{Definition of symbols and variables}
\centering
\begin{tabular}{l c c}
\hline
 Variable & Description & Units  \\
\hline
$e_s$  & saturation vapor pressure & Pa  \\ 
$T$  & temperature  & K \\
$\Delta$  & $\frac{\partial e_s}{\partial T}$ & Pa K$^{-1}$ \\
$R$  & net radiation at land surface minus ground heat flux & W m$^{-2}$   \\
  $g_a$  & atmospheric conductance & m s$^{-1}$  \\
  $\rho_a$  & air density & kg m$^{-3}$  \\
  $c_p$  & specific heat capacity of air at constant pressure & J K$^{-1}$ kg$^{-1}$ \\
  $D$  & VPD & Pa  \\
  $\gamma$  & psychrometric constant & Pa K$^{-1}$   \\
  $g_s$  & stomatal conductance & m s$^{-1}$  \\
  $g_{l-s}$  & leaf-scale stomatal conductance & mol m$^{-2}$ s$^{-1}$  \\
  $R*$ & universal gas constant & J mol$^{-1}$ K$^{-1}$ \\
  $LAI$ & leaf area idex & -\\
\hline
\multicolumn{2}{l}{$^{a}$Footnote text here.}
\end{tabular}
\end{table}

@@

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig01.pdf}
\caption{Plant functional type and location of sites used in analysis. Note should probably just split this into 4 continents (US, Europe, Africa, Australia).}
\label{map_fig}
 \end{figure}

@@

>>>>

\begin{table}
\caption{Definition of symbols and variables}
\centering
\begin{tabular}{l c c}
\hline
 Variable & Description & Units  \\
\hline
$e_s$  & saturation vapor pressure & Pa  \\ 
$T$  & temperature  & K \\
$\Delta$  & $\frac{\partial e_s}{\partial T}$ & Pa K$^{-1}$ \\
$R$  & net radiation at land surface minus ground heat flux & W m$^{-2}$   \\
  $g_a$  & atmospheric conductance & m s$^{-1}$  \\
  $\rho_a$  & air density & kg m$^{-3}$  \\
  $c_p$  & specific heat capacity of air at constant pressure & J K$^{-1}$ kg$^{-1}$ \\
  $D$  & VPD & Pa  \\
  $\gamma$  & psychrometric constant & Pa K$^{-1}$   \\
  $g_s$  & stomatal conductance & m s$^{-1}$  \\
  $g_{l-s}$  & leaf-scale stomatal conductance & mol m$^{-2}$ s$^{-1}$  \\
  $R*$ & universal gas constant & J mol$^{-1}$ K$^{-1}$ \\
  $LAI$ & leaf area index & -\\
  $c_s$ & CO$_2$ concentration & $\mu$ mol CO$_2$ mol$^{-1}$ air\\
\hline
\multicolumn{2}{l}{$^{a}$Footnote text here.}
\end{tabular}
\end{table}

@@

\begin{figure}[h]
\centering
\includegraphics[width=20pc]{./fig01.pdf}
\caption{Plant functional type and location of sites used in analysis. Note should probably just split this into 4 continents (US, Europe, Africa, Australia).}
\label{map_fig}
 \end{figure}p

@@

\begin{table}
\caption{Statistics of $\frac{\partial \; ET}{\partial \; D}$ as a function of PFT.}
\centering
\begin{tabular}{l c c c c c}
  \hline
PFT & $\overline{\frac{\partial \; ET}{\partial \; VPD}}$ & $\frac{\partial \; ET}{\partial \; D}\left(\overline{T, \ldots , D}\right)$ & $\frac{\partial \; ET}{\partial \; D}\left(\overline{T, \ldots , D}\right)*\text{std}(D)$ & $\frac{\frac{\partial \; ET}{\partial \; D}\left(\overline{T, \ldots , D}\right)*\text{std}(D)}{ \frac{\partial \; ET}{\partial \; R}\left(\overline{T, \ldots , D}\right)*\text{std}(R)}$ & fraction $\frac{\partial \; ET}{\partial \; VPD} < 0.$ \\
  \hline
CRO & 0.000853 & 0.026241 & 18.523659 & 0.203022 & 0.473311\\
CSH & -0.108234 & -0.091526 & 50.861613 & 0.439379 & 0.931660\\
DBF & -0.012727 & 0.013794 & 19.734435 & 0.164241 & 0.461674\\
ENF & -0.034087 & 0.000706 & 16.611852 & 0.148548 & 0.534425\\
GRA & -0.019637 & -0.000921 & 16.798083 & 0.173552 & 0.631735\\
\hline
\multicolumn{2}{l}{$^{a}$Footnote text here.}

\end{tabular}
\end{table}
